Title page

### 2024-09-16 output/Title_page.Rmd
Update title page
Update styles in title page to avoid indentation

---
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

@@

# Statements and Declarations

## Ethical considerations

Not applicable

## Consent to participate

Not applicable

## Consent for publication

Not applicable

## Declaration of conflicting interest

The author(s) declared no potential conflicts of interest with respect to
the research, authorship, and/or publication of this article.

## Funding statement

Not applicable

## Data availability statement

Not applicable

>>>>

---
output:
  officedown::rdocx_document:
    mapstyles:
      First Paragraph: Body Text
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

@@

# Financial Support

This research received no specific grant funding form any funding agency,
commercial or not-for-profit sectors.

# Competing Interests Statement

Competing interests: The author(s) declare none.
